\sysfull

### 2017-08-10 paper/compiler.tex
fixed some points due to red text

The input to the task boundary identification analysis is a standard C program (as shown in Figure~\ref{fig:comp_1}) and the output of \sys's analysis is the CFG, with some vertices marked as {\em task boundaries}. The \sys compiler builds the program's CFG (as shown in
Figure~\ref{fig:comp_2}). To simplify inter-procedural analysis, our prototype inlines all function calls\todo{how about recursions and code duplication?}{Brandon/Kiwan} into the main function in the CFG.
%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%
We first describe how \sys measures each of these costs and then describe \sys's procedure for placing boundaries in the CFG.

@@

{\noindent \bf Live variable cost.} Each CFG edge is associated with a set of {\em live variables} that are accessed in both\todo{Transitive closure?}{Brandon/Kiwan} of the blocks that define the edge (i.e., predecessor and successor). Variables that live across an edge between two tasks must be protected by \sys's memory virtualization mechanism and each live, inter-task variable increases the run time overhead for a boundary placement. \sys's tries to minimize the overhead of protected variables by placing boundaries to minimize the number of inter-task live variables.

>>>>

The input to the task boundary identification analysis is a standard C program (as shown in Figure~\ref{fig:comp_1}) and the output of \sys's analysis is the CFG, with some vertices marked as {\em task boundaries}. The \sys compiler builds the program's CFG (as shown in
Figure~\ref{fig:comp_2}). To simplify inter-procedural analysis, our prototype inlines all function calls into the main function in the CFG. Recursive function call cannot be handled, so the programmer has to rewrite it into a non-recursive call if there is one. The approach of always inlining function calls will introduce code duplication. If the code size is problematic, alternative approach is to make each function call a task boundary. We leave implementation of such alternative strategy as a future work.
%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%
We first describe how \sys measures each of these costs and then describe \sys's procedure for placing boundaries in the CFG.

@@

{\noindent \bf Live variable cost.} Each CFG edge is associated with a set of variable that {\em may} be {\em alive} across the edge (i.e., variables whose value may be consumed later on). Variables that live across an edge must be protected by \sys's memory virtualization mechanism and each protected, inter-task variable increases the run time overhead for a boundary placement. \sys's tries to minimize the overhead of protected variables by placing boundaries to minimize the number of inter-task live variables.
